---
title: "Rice RAPDB to MSU7 ID conversion"
author: "Ji Huang"
date: '2019-04-03'
comment: no
contentCopyright: no
categories: dry lab
description: ''
keywords: []
lastmod: '2019-04-03T16:53:12-04:00'
mathjax: no
mathjaxEnableSingleDollar: no
postMetaInFooter: no
reward: no
slug: rice-rapdb-to-msu7-id-conversion
tags:
- rice
- R
autoCollapseToc: no
toc: no
---

In this post, I generate the table for **RAPDB** gene IDs and **MSU7** gene IDs conversion.

<!--more-->

There are some online tools can do the conversion, but it's more handy to have a local version. One online tool is [RAP-DB ID Converter](https://rapdb.dna.affrc.go.jp/tools/converter). The other is [OryzaExpress ID converter](http://bioinf.mind.meiji.ac.jp/OryzaExpress/ID_converter.php).

The conversion table was downloaded from [RAPDB](https://rapdb.dna.affrc.go.jp/download/irgsp1.html) on 2019-04-03.



# 0. Set up environment.

```{r load_libs, include=FALSE}
library(tidyverse)
```

# 1. Read data

```{r file_path, include=FALSE}
table_path <- "I:/#project/Google Drive (jh6577@nyu.edu)/Project/rice_tables/RAP-MSU_2019-03-22.txt"
```

The `table_path` was hided.

```{r read_table}
# read raw downloaded table.
c_table <- read_tsv(table_path, col_names = c("RAPDB", "MSU"))
```


# 2. Process table.

Get RAPDB gene ID correspondent MSU7 IDs. The MSU7 transcript ID was converted to Gene ID by removing **.[digits]**.

```{r process_table}
cp_table <- c_table %>% separate_rows(MSU,sep = ",") %>%  
    mutate(MSU7 = str_replace(.$MSU,"\\.[:digit:]+","")) %>% 
    select(-MSU) %>% 
    distinct(RAPDB, MSU7)
```

There are **`r length(unique(c_table$RAPDB))`** RAPDB genes. And **`r length(unique(cp_table$MSU))`** MSU7 genes.


# 3. Save table.

```{r save_table, eval=FALSE}
write_tsv(cp_table, path = "./RAPDB_MSU_ID_conversion_20190403.txt")
```

# 3. Some exploratory analysis.

1. How many RAPDB genes don't have MSU7 genes, as indicated by **None** in the `MSU` column?

```{r rapdb_noMSU}
sum(cp_table$MSU7 == "None")
```

2. How many MSU7 genes don't have RAPDB IDs, as indicated by **None** in the `RAPDB` column?

```{r msu_noRAPDB}
sum(cp_table$RAPDB == "None")
```

3. How many RAPDB genes have multiple MSU7 genes?

The first number should minus 1, because there is one item named *None*.
```{r rapdb_multiMSU}
cp_table %>% group_by(RAPDB) %>% tally() %>% filter(n > 1) %>% 
    dim() %>% magrittr::extract(1) -1
```

4. How many MSU7 genes have multiple RAPDB genes?

```{r msu_multiRAPDB}
cp_table %>% group_by(MSU7) %>% tally() %>% filter(n > 1) %>% 
    dim() %>% magrittr::extract(1) -1
```

